---
title: "Smoking Trends in UK"
author: "Khush Dakwala and Max McGinn"
format: revealjs
editor: visual
---

## Introduction

We are trying to see how smoking habits differ in people. We will be analyzing different smoking trends in the UK based on different points like:

-   Demographics

-   Smoking Status (Yes/No)

-   Amount smoked on Weekends and Weekdays

-   Type of Smoking

## Smoking Status Distribution in the UK

```{r}
library(ggplot2)

# Load the dataset
data <- read.csv("smoking.csv")

# Calculate proportions
data_prop <- as.data.frame(table(data$smoke))
colnames(data_prop) <- c("smoke", "count")
data_prop$percent <- data_prop$count / sum(data_prop$count)

# Create the bar plot with percentages
plot <- ggplot(data_prop, aes(x = smoke, y = percent, fill = smoke)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Smoking Status Distribution", x = "Smoking Status (Yes/No)", y = "Percentage") +
  theme_minimal() +
  theme(legend.position = "none")

# Print the plot
print(plot)

```

## Smoking by Gender

```{r}
library(ggplot2)

# Bar plot showing percentage of smokers/non-smokers by gender
ggplot(data, aes(x = gender, fill = smoke)) +
  geom_bar(position = "fill") +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(
    title = "Smoking Status by Gender (Percentage)",
    x = "Gender",
    y = "Percentage",
    fill = "Smoker"
  ) +
  theme_minimal()
```

**/Age/**

Min-16 / Max- 97 Q1-34 Median-48/ Mean-49.84 Q3- 65

**/Amount on Weekends/ /Amount of Weekdays/**

Q1- 10 Median- 15 Q3- 20 Q1-7 Median- 12 Q3- 20

Mean= 16.41 Mean= 13.75
